\bf Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-03 paper.qmd
language smoothing

To estimate the underlying normal distribution the data is first centered and scaled using the median and the median absolute deviation (MAD), before applying the minimum covariance determinant (MCD) estimator @rousseeuw1985multivariate using the implementation in @robustbase. The MCD estimates for the mean vector and the variance-covariance matrix are then used to define the reference normal distribution.

>>>>

To estimate the underlying normal distribution the data is first centered and scaled using the median and the median absolute deviation (MAD), before applying the minimum covariance determinant (MCD) estimator [@rousseeuw1985multivariate] using the implementation in @robustbase. The MCD estimates for the mean vector and the variance-covariance matrix are then used to define the reference normal distribution.

### 2024-07-03 paper.tex
language smoothing

Another application would compare outlying points to a reference normal
distribution that is derived using robust methods on the original data.
To illustrate this we work on the weather data example from
\citet{filzmoser2018}. The data contains 16 numerical measurements that
are averages across the three summer months June, July and August, these
are provided for 68 years (1955 - 2022), see \citet{filzmoser2018} for
more details.

To estimate the underlying normal distribution the data is first
centered and scaled using the median and the median absolute deviation
(MAD), before applying the minimum covariance determinant (MCD)
estimator \citet{rousseeuw1985multivariate} using the implementation in
\citet{robustbase}. The MCD estimates for the mean vector and the
variance-covariance matrix are then used to define the reference normal
distribution.

>>>>

This example is motivated by the weather data example from
\citet{filzmoser2018}. We illustrate using the anomaly index to compare
potential outliers with a reference normal distribution that is derived
using robust methods on the original data. The data contains 16
numerical measurements that are averages across the three summer months
June, July and August, these are provided for 68 years (1955 - 2022),
see \citet{filzmoser2018} for more details.

To estimate the underlying normal distribution the data is first
centered and scaled using the median and the median absolute deviation
(MAD), before applying the minimum covariance determinant (MCD)
estimator \citep{rousseeuw1985multivariate} using the implementation in
\citet{robustbase}. The MCD estimates for the mean vector and the
variance-covariance matrix are then used to define the reference normal
distribution.
